Design and Implementation of Probabilistic Programming Language Anglican

### 2017-02-21 paper/paper.tex
update

\texttt{sample} and \texttt{observe} forms correspond to
handling $(F, \alpha)$ and $(G, y)$ correspondingly in the
definition of probabilistic program (Section~\ref{sec:pp-def}).
Their operational semantics can be defined in terms of
importance sampling(Equation~\ref{eqn:p-trace}): 
\begin{itemize}
    \item \texttt{sample} returns a value drawn from
        the distribution.
    \item \texttt{observe} multiplies the unnormalized
        probability of the program trace by the probability of
        drawing the value from the distribution.
\end{itemize}
However, the actual computation involved in handling of
\texttt{sample} and \texttt{observe} depends on the inference
algorithm. Different inference algorithms may treat
\texttt{sample} and \texttt{observe} differently as long as they
compute the same distribution of program results.
Denotational and operational semantics for an idealized version
of Anglican is introduced in \cite{SYH+16}; in general though,
specifying semantics of higher-order probabilistic programming
languages is an open problem.

>>>>

A good way to understand the \texttt{sample} and \texttt{observe} forms
is to consider the imaginary interpreter in Section~\ref{sec:pp-def}.
Under this interpreter, the \texttt{sample} form draws a value $x$ from 
its parameter distribution $F$, and 
generates a unique address $\alpha$ for this random draw.
Then, it appends $(F, x, \alpha)$, the record of this random
draw, to the log of the current execution. Finally, the
form returns $x$. The computation of the \texttt{observe} form is
simpler. It just appends its two parameters, distribution $G$
and observed value $v$, to the log of the current execution,
and returns \texttt{nil}.

What we have just described is idealised semantics 
of \texttt{sample} and \texttt{observe}. The actual computation 
involved in handling \texttt{sample} and \texttt{observe} 
depends on the inference algorithm. Different inference algorithms may treat
\texttt{sample} and \texttt{observe} differently as long as they
compute the same distribution on traces (i.e. sequences of sampled values), 
namely, the one in Equation~\ref{eqn:p-trace}.
Formal semantics for an idealized version
of Anglican or other higher-order probabilistic programming languages are introduced 
in \cite{SYH+16,BorgstromLGS16}; in general though,
specifying semantics of higher-order probabilistic programming
languages is an open problem.

%Their operational semantics can be defined in terms of
%importance sampling(Equation~\ref{eqn:p-trace}): 
%\begin{itemize}
%    \item \texttt{sample} returns a value drawn from
%        the distribution.
%    \item \texttt{observe} multiplies the unnormalized
%        probability of the program trace by the probability of
%        drawing the value from the distribution.
%\end{itemize}
%However, the actual computation involved in handling of
%\texttt{sample} and \texttt{observe} depends on the inference
%algorithm. Different inference algorithms may treat
%\texttt{sample} and \texttt{observe} differently as long as they
%compute the same distribution of program results.
%Denotational and operational semantics for an idealized version
%of Anglican is introduced in \cite{SYH+16}; in general though,
%specifying semantics of higher-order probabilistic programming
%languages is an open problem.
